On exponential sums arising from the classical doubling method

### 2025-04-11 main.tex
Corrections/clarifications

		\end{smallmatrix}\right) \in \GL_2\left(\finiteFieldExtension{n}\right)$and $$\Frobenius\left(z\right) = \left(\Frobenius x, \Frobenius y\right) = \left(x^q,y^q\right).$$ Then $\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}}$ is realized as the subgroup of $\GL_{2n}\left(\finiteFieldExtension{n}\right) \times \GL_{2n}\left(\finiteFieldExtension{n}\right)$ given by the image of the map $$z \mapsto \left(\diag\left(Dz,D\Frobenius^2 z,\dots, D\Frobenius^{n-2} z\right), \diag\left(D\Frobenius z, D\Frobenius^3 z, \dots, D\Frobenius^{n-1} z\right)\right),$$

@@

For different tori with Frob action we get

@@

The results now follow from these equalities, since we can easily find a permutation matrix in $\GL_{2n}$ that conjugates the character that corresponds to $\phi\left(x_{T,\bullet}\right)$ to the desired character from the proposition. This permutation matrix simply corresponds to the permutation that permutes the $y_i$'s so that $q^i$ is the coefficient of $y_{i+1}$ in the exponent of the right hand side of the corresponding equation for every $0 \le i \le 2n-1$.

>>>>

		\end{smallmatrix}\right) \in \GL_2\left(\finiteFieldExtension{n}\right)$and $$\Frobenius\left(z\right) = \left(\Frobenius x, \Frobenius y\right) = \left(x^q,y^q\right).$$ Then $\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}}$ is realized as the subgroup of $\restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\algebraicGroup{\GL}_n}\left(\finiteFieldExtension{n}\right) = \GL_{n}\left(\finiteFieldExtension{n}\right) \times \GL_{n}\left(\finiteFieldExtension{n}\right)$ given by the image of the map $$z \mapsto \left(\diag\left(Dz,D\Frobenius^2 z,\dots, D\Frobenius^{n-2} z\right), \diag\left(D\Frobenius z, D\Frobenius^3 z, \dots, D\Frobenius^{n-1} z\right)\right),$$

@@

For different tori with $\Frobenius$ actions we get

@@

The results now follow from these equalities and the norm computations, since we can easily find a permutation matrix in $\GL_{2n}$ that conjugates the character that corresponds to $\phi\left(x_{T,\bullet}\right)$ to the desired character from the proposition. This permutation matrix simply corresponds to the permutation that permutes the $y_i$'s so that $q^i$ is the coefficient of $y_{i+1}$ in the exponent of the right hand side of the corresponding equation for every $0 \le i \le 2n-1$.
